\textbf{Hardware accelerator topologies in heterogeneous systems: an evaluation in the security domain}

### 2019-12-07 reports/paper.tex
write more

@@

Going one step further than the two classic topologies used for accelerators
discussed previously, we present a slightly different hybrid approach which has
some interesting characteristics. Figure~\ref{fig:hybrid} shows the concept and
possible operation modes of the hybrid crypto accelerator.

>>>>

The Simon family of ciphers offers different possibilities for both block and
key sizes. In all cases, both the round and key expansion functions make use
only of bitwise \texttt{XOR}, \texttt{AND}, and left and right circular shifts.
Figure~\ref{fig:simonround} shows the Feistel stepping of its round function.

\begin{figure}
  \centering
  \include{media/simonround}
  \caption{Simon's round function Feistel stepping. \textbf{S\textsuperscript{i}} are
    circular left shifts by i bits; \textbf{\&} is a bitwise \texttt{AND}
    operation and $\oplus$ are bitwise \texttt{XOR} operations.}
  \label{fig:simonround}
\end{figure}

The number of necessary rounds is determined by the configuration of the cipher.
In this work we explore only the Simon64/128 and Simon128/128 configurations,
which require a number of 44 and 68 rounds per block, respectively.
In the nomenclature Simon\textbf{N}/\textbf{M}, \textbf{N} is the block size and
\textbf{M} is the key size in bits.

@@

Going one step further than the two previously discussed topologies used for
accelerators, we present a slightly different hybrid approach which has
some interesting characteristics. Figure~\ref{fig:hybrid} shows the concept and
possible operation modes of the hybrid crypto accelerator.
